### 2017-04-13 paper/oopsla17-submission/intro2.tex
asd

\section{Introduction}
\label{sec:introduction}

% In Robin Milner's memorable words
% %
% ``types are the leaven of computer programming;
  % they make it digestible''~\cite{tapl}.
%
Types are awesome.
%
Languages like \ocaml and \haskell make
the value-proposition for types even more
appealing by using constraints to automatically
synthesize the types for all program terms
without troubling the programmer for any
annotations.
%
Unfortunately, this automation has come at a price.
Verbose type annotations (as in, \eg, \java) signify
the programmer's intent and help to correctly
blame the erroneous sub-term when the code is
ill-typed.
%
In the absence of such signifiers, automatic
type inference algorithms are prone to report
type errors far from their actual source
\citep{Wand1986-nw}.
%
While this can seem like a minor annoyance to
veteran programmers, \citet{Joosten1993-yx} have found
that novices often focus their attention on the \emph{location}
reported and disregard the \emph{message}.

\mypara{Localizing Errors}
%
Several recent papers have proposed ways
to improve feedback via error \emph{localization}.
%
At a high-level these techniques analyze
the set of typing constraints to find
the minimum (weighted) subset that,
if removed would make the constraints
satisfiable and hence, memory-safe~\citep{Jose:2011}
or well-typed~\citep{Zhang2014-lv,Loncaric2016-uk,Chen2014-gd,Pavlinovic2014-mr}.
The finger of blame is then pointed at the
sub-terms that yielded those constraints.
%
This minimum-weight approach suffers
from two drawbacks.
%
First, they are not \emph{extensible}:
% the weights and analyses are limited
% to attributes of the constraints, and
% not other \emph{signals} from the
% program's syntax that may be more
% germane to error localization. Furthermore,
the constraint languages and algorithms for computing
the minimum weighted subset must be
designed afresh for different kinds
of type systems and constraints \citep{Loncaric2016-uk}.
%
Second, and perhaps most importantly,
they are not \emph{adaptable}: the
weights are fixed in an ad-hoc fashion, based on the
\emph{analysis designer's} notion
of what kinds of errors are more
or less likely, rather than
adapting to the kinds of mistakes
programmers actually make in practice.

\mypara{A Data-Driven Approach}
%
In this paper, we introduce \toolname
\footnote{``Numeric Analysis of Type Errors''; any resemblance to persons living or dead is purely coincidental.}
a \emph{data-driven} approach to error
localization based on supervised
learning (see \citealt{Kotsiantis2007-pj} for a survey).
%
\toolname works by analyzing a large corpus
of training data --- pairs of ill-typed
programs and their subsequent fixes ---
to automatically \emph{learn a model}
of where errors are most likely to
be found.
%
Given a new ill-typed program,
\toolname simply executes the model
to generate a list of potential error
locations ranked by likelihood.
%
We evaluate \toolname by comparing its
precision against the state-of-the-art
on a set of over 4,500 ill-typed \ocaml
programs drawn from introductory
programming classes.
%
We show that \toolname's data-driven
model is able to correctly predict
the exact sub-expression that needs to
be changed 74\% of the time,
29 points higher than \ocaml and
18 points higher than the state-of-the-art
\sherrloc tool.
%
Further, \toolname's accuracy surpasses
85\% when we consider the \emph{top two}
locations and reaches 91\% if consider
the \emph{top three}.
%
We achieve these advances by identifying
and then solving three key challenges.

\mypara{Challenge 1: Acquiring Labeled Programs}
%
The first challenge for supervised learning
is to acquire a corpus of training data, in our setting
a set of ill-typed programs \emph{labeled}
with the exact sub-terms that are the actual
cause of the type error.
%
Prior work has often enlisted expert users
to manually judge ill-typed programs and
determine the ``correct'' fix
\citep[\eg][]{Lerner2007-dt,Loncaric2016-uk},
but this approach does not scale well to
a dataset large enough to support machine
learning.
%
Worse, while expert users have intimate
knowledge of the type system, they may
have a blind spot with regards to the
kinds of mistakes novices make, and
cannot know in general what novice users
intended.

Our \emph{first contribution} (\autoref{sec:overview})
is a set of more than 4,500 labeled programs,
gives us an accurate ground truth of
the kinds of errors and the (locations
of the) fixes that novices make in
practice.
%
We obtain this set by observing that
software development is an iterative
process; programmers eventually
fix their own ill-typed programs,
perhaps after multiple incorrect
exploratory attempts.
%
To exploit this observation we instrumented
the \ocaml compiler to collect fine-grained
traces of student interactions over two instances
of an undergraduate Programming Languages
course.\footnote{
% \begin{anonsuppress}
% UC San Diego (IRB \#140608).
% \end{anonsuppress}
% \begin{noanonsuppress}
at AUTHOR's INSTITUTION (IRB HIDDEN).
% \end{noanonsuppress}
}
%
We then post-process the resulting time-series
of programs submitted to the \ocaml compiler into
a set of pairs of ill-typed programs and their
subsequent \emph{fixes}, the first (type-)~correct
program in the trace suffix.
%
Finally, we label the changed locations by computing a
\emph{tree-diff} between the two terms to find
the exact sub-terms that were changed in the fix.

\mypara{Challenge 2: Modeling Programs as Vectors}
%
Modern supervised learning algorithms work on %sets of
\emph{feature vectors}: real-valued points in an
$n$-dimensional space. While there are standard
techniques for computing such
vectors for documents, images, and sound (respectively
word-counts, pixel-values, and frequencies),
% it has
% hitherto been unclear how to precisely model program
% structure as numeric data.
there are no similarly standard representations for
programs.

Our \emph{second contribution} (\autoref{sec:learning})
solves this problem with a simple, yet expressive, representation called
a \emph{Bag-of-Abstract-Terms (BOAT)} wherein
%
(1)~each program is represented by the \emph{bag}
    or multiset of (sub-)~terms that appears inside
    it; and
%
(2)~each (sub-)~term $t$ is \emph{abstracted} as
    a vector $[f_1(t), \ldots, f_n(t)]$, where
    each $f_i$ is a \emph{feature abstraction}
    that maps a term to a numeric value.
%
We can model the error labels with a simple feature
abstraction (\eg does-change-in-fix).
%
We can even account for \emph{contextual} information like
the features of the parent- and child- terms by
concatenating the feature vectors of each term with those
of its parent and children.
%
We have found this representation to be particularly
convenient as it gives us flexibility
in modeling the syntactic and semantic structure of programs
while retaining compatibility with off-the-shelf classifiers,
in contrast to, \eg, \citet{Raychev2015-jg}, who had to develop
their own variants of classifiers to obtain their results.

\mypara{Challenge 3: Training Precise Classifiers}
%
Finally, the last and most important challenge is to
use the labeled BOAT data to train classifiers that
are capable of \emph{precisely} pinpointing the error
locations in real programs.
%
The key here is to find the right set of feature
abstractions and classification algorithms, that
lead to precise predictions.
%
Fortunately, our BOAT model allows us a great deal of
latitude in our choice of features.
%
We can use abstraction functions to capture different
aspects of a term ranging from
%
syntactic features (\eg is-a-data constructor, is-a-literal,
is-an-arithmetic-operation, is-a-function-application, \etc),
%
to semantic features captured by the type system (\eg is-a-list,
is-an-integer, is-a-function, \etc).

Our \emph{third contribution} (\autoref{sec:evaluation})
is a systematic evaluation of our data-driven approach
using different classes of features like the above, and
with three different classification algorithms: logistic
regression, decision trees, and neural networks.
%
Our evaluation lets us identify the best features and
classifier and empirically characterize the importance
of different features for error localization.
%
In particular, we find that while machine learning
over syntactic features of each term in isolation
performs worse than existing
purely constraint based approaches (\eg \ocaml, \sherrloc),
augmenting the data with a single feature corresponding to
the \emph{type error slice} \citep{Tip2001-qp} brings our
classifiers up to par with the state of the art,
and further augmenting the data with \emph{contextual}
features allows our classifiers to outperform
the state of the art by 18 percentage points.
% In particular, we find that while machine learning
% on its own performs slightly worse than existing
% purely constraint based approaches (\eg \ocaml, \sherrloc),
% once we augment the data with feature abstraction
% corresponding to the \emph{type error slice} \citep{Tip2001-qp},
% the resulting classifier significantly outperforms the
% state of the art by 18 percentage points.

>>>>

\section{\textbf{Introduction}}
\label{sec:introduction}

% In Robin Milner's memorable words
% %
% ``types are the leaven of computer programming;
  % they make it digestible''~\cite{tapl}.
%
Types are awesome.
%
Languages like \ocaml and \haskell make
the value-proposition for types even more
appealing by using constraints to automatically
synthesize the types for all program terms
without troubling the programmer for any
annotations.
%
Unfortunately, this automation has come at a price.
Verbose type annotations (as in, \eg, Java) signify
the programmer's intent and help to correctly
blame the erroneous sub-term when the code is
ill-typed.
%
In contrast, lacking such signifiers, automatic
type inference algorithms are prone to report
type errors quite far from their actual source.
%
While this can seem like a minor annoyance to
veteran programmers, it turns out to be a significant
stumbling block for novices~\citep{Wand1986-nw,Joosten1993-yx}.

\mypara{Localizing Errors}
%
Several recent papers have proposed ways
to improve feedback via error \emph{localization}.
%
At a high-level these techniques analyze
the set of typing constraints to find
the minimum (weighted) subset that,
if removed would make the constraints
satisfiable and hence, memory-safe~\citep{Jose:2011}
or well-typed~\citep{Zhang2014-lv,Loncaric2016-uk,Chen2014-vm,Pavlinovic2014-mr}.
The finger of blame is then pointed at the
sub-terms that yielded those constraints.
%
This minimum-weight approach suffers
from two drawbacks.
%
First, they are not \emph{extensible}:
the weights and analyses are limited
to attributes of the constraints, and
not other \emph{signals} from the
program's syntax that may be more
germane to error localization. Furthermore,
the algorithms for computing
the minimum weighted subset must be
designed afresh for different kinds
of type systems and constraints.
%
Second, and perhaps most importantly,
they are not \emph{adaptable}: the
weights are fixed in an ad-hoc fashion, based on the
\emph{analysis designers} notion
of what kinds of errors are more
or less likely, rather than
adapting to the kinds of mistakes
programmers actually make in practice.

\mypara{A Data-Driven Approach}
%
In this paper, we introduce \toolname
\footnote{``Numeric Analysis of Type Errors''; any resemblance to persons living or dead is purely coincidental.}
a \emph{data-driven} approach to error
localization based on supervised
classification~\citep{Kotsiantis2007-pj}.
%
\toolname works by using a large corpus
of training data --- pairs of ill-typed
programs and their fixed versions ---
to automatically \emph{learn a model}
of where the error is most likely.
%
When given a new ill-typed program,
\toolname simply executes the model
to generate a list of likely error
locations ranked by likelihood.
%
We evaluate \toolname by comparing its
precision against the state-of-the-art
on a set of over 4,500 ill-typed Ocaml
programs drawn from introductory
programming classes.
%
We show that \toolname's data-driven
model is able to correctly predict
the exact sub-expression that needs to
be changed, 74\% of the time, which is
29 points higher than \ocaml, and
18 points higher than the state-of-the-art
\sherrloc tool.
%
Further, \toolname's accuracy surpasses
85\% when we consider the \emph{top-2}
locations and reaches 91\% if consider
the \emph{top-3}.
%
We achieve these advances by identifying
and then solving three key challenges.

\mypara{Challenge 1: Acquiring Labeled Programs}
%
The first challenge for supervised learning
is to acquire a corpus of training data, here,
a set of ill-typed programs \emph{labeled}
with the exact sub-terms that are the actual
cause of the type error.
%
Prior work has often enlisted expert users
to manually judge ill-typed programs and
determine the ``correct'' fix \citep[\eg][]{Loncaric2016-uk},
but this approach does not scale well to
a dataset large enough to support machine
learning.
%
Worse, while expert users have intimate
knowledge of the type system, they may
have a blind spot with regards to the
kinds of mistakes novices make, and
cannot know in general what novice users
intended.

Our \emph{first contribution} (\autoref{sec:overview})
is a set of more than 4,500 labeled programs,
gives us an accurate ground truth of
the kinds of errors and the (locations
of the) fixes that novices make in
practice.
%
We obtain this set by observing that
software development is an iterative
process and programmers eventually
fix their own ill-typed programs,
perhaps after multiple incorrect
exploratory attempts.
%
To exploit this observation we instrumented
the \ocaml compiler to collect fine-grained
traces of student interactions over two instances
of an undergraduate Programming Languages course
%
\footnote{
% \begin{anonsuppress}
% UC San Diego (IRB \#140608).
% \end{anonsuppress}
% \begin{noanonsuppress}
at AUTHOR's INSTITUTION (IRB HIDDEN).
% \end{noanonsuppress}
}
%
We can then post-process the resulting time-series
of programs submitted to the \ocaml compiler into
a set of pairs of ill-typed programs and their
\emph{fixed} versions, the \emph{first} (type-)correct
program in the trace suffix.
%
We obtain the location labels by computing a
\emph{tree-diff} between the two terms to find
the exact sub-terms that were changed in the fix.

\mypara{Challenge 2: Modeling Programs as Vectors}
%
Modern supervised learning algorithms work on sets of
\emph{feature vectors}: real-valued points in an
$n$-dimensional space. While it is easy to compute such
vectors for documents, images and sound (respectively
word-counts, pixel-values and frequencies), it has
hitherto been unclear how to precisely model program
structure as numeric data.

Our \emph{second contribution} (\autoref{sec:learning})
solves this problem with a new representation called
a \emph{Bag-of-Abstract-Terms (BOAT)} wherein
%
(1)~each program is represented by the \emph{bag}
    or multiset of (sub-)terms that appears inside
    it, and
%
(2)~each (sub-)term $t$ is \emph{abstracted} as
    a vector $[f_1(t), \ldots, f_n(t)]$ where
    each $f_i$ is a \emph{feature abstraction}
    that maps a term to a numeric value.
%
We can model the error labels with a simple feature
abstraction (\eg is-a-diff-subterm).
%
We can even account for \emph{contextual} information like
the features of the parent- and children- terms by
concatenating the feature vectors of each term with those
of its parent and children.

\mypara{Challenge 3: Training Precise Classifiers}
%
Finally, the last and most important challenge is to
use the labeled BOAT data to train classifiers that
are capable of \emph{precisely} pinpointing the error
locations in real programs.
%
The key here is to find the right set of feature
abstractions and classification algorithms, that
lead to precise predictions.
%
Fortunately, our BOAT model allows us a great deal of
latitude in our choice of features.
%
We can use abstraction functions to capture different
aspects of a term ranging from
%
syntactic features (\eg is-a-data constructor, is-a-literal,
is-an-arithmetic-operation, is-a-function-application \etc),
%
to semantic features captured by the type system (\eg is-a-list,
is-an-integer, is-a-function \etc).

Our \emph{third contribution} (\autoref{sec:evaluation})
is a systematic evaluation of our data-driven approach
using different classes of features like the above, and
with three different classification algorithms: linear
classifiers, decision forests and deep neural networks.
%
Our evaluation lets us identify the best features and
classifier and empirically characterize the importance
of different features for error localization.
%
In particular, we find that while machine learning
on its own performs slightly worse than existing
purely constraint based approaches (\eg \ocaml, \sherrloc),
once we augment the data with feature abstraction
corresponding to the \emph{type error slice} \cite{Tip2001-qp},
the resulting classifier significantly outperforms
state-of-the-art by 18 percentage points.

### 2017-04-13 paper/oopsla17-submission/overview.tex
asd

\section{Overview}
\label{sec:overview}

We start with an overview of our approach to localizing type errors by
learning a model of the mistakes programmers actually make.
%
We formulate the problem of type error localization as a
\emph{supervised classification} problem (see \citealt{Kotsiantis2007-pj}
for a survey).
%
A \emph{classification} problem entails learning a function that maps
inputs to a discrete set of output \emph{labels}, in contrast to
\emph{regression}, where the output is typically a real number.
%
In a \emph{supervised} learning problem one is given a \emph{training}
set where the inputs and labels are known, and the task is to learn a
function that accurately maps the inputs to outputs and
\emph{generalizes} to new, yet-unseen inputs.

The key technical challenges we address are:
%
(1) formulating type error localization as a classification problem;
%
%(2) generating correct labels for supervised learning; and
(2) identifying ``correct'' blame assignments in our dataset; and
%
(3) presenting the predictions of the classifier in an intuitive manner.

\paragraph{\textbf{Challenge (1): How to represent programs?}}
The first and prime challenge we address is how to translate programs
into a format favorable to learning a model of type errors.
%
Programs can be represented in various ways, from the raw text to 
richly-structured abstract syntax trees and control-flow graphs, but 
many representations are not directly amenable to machine learning.
%
Furthermore, program representations that are amenable to one learning
task, \eg code completion, may not be favorable to our problem of
assigning blame for type errors.

@@

\paragraph{\textbf{Challenge (2): What is the ``correct'' expression to blame?}}
As we saw in \autoref{fig:sumList}, type errors admit many different
fixes to different expressions, each resulting in a different program.
%
How is the type checker to judge which expressions are more likely to be
incorrect than others?
%
Prior work has often enlisted expert users to manually judge ill-typed
programs and determine the ``correct'' fix
\citep[\eg][]{Loncaric2016-uk}, but this approach does not scale well to
a dataset large enough to support machine learning.
%
Furthermore, while expert users have intimate knowledge of the type system,
they cannot know in general what novice users \emph{intended} to do.

\paragraph{\textbf{Solution: Use the students' subsequent fixes}}
%
Rather than relying on expert users, we allow our students to do the
work of assigning blame themselves.
%
Software development is an iterative process and our students 
eventually fix their own programs, perhaps after multiple ill-fated
attempts.
%
For each ill-typed program in our dataset, we find the first
\emph{subsequent} program that type checks and declare that to be the
fix.
%
From this pair of an ill-typed program and its fix, we can extract a
\emph{diff} of the abstract syntax trees.
%
For example, suppose our student fixed the |sumList| program in
\autoref{fig:sumList} by replacing |[]| with |0|, the diff would include
only the |[]| expression.
%
Thus we would determine that the |[]| expression (and \emph{not} the
|+| or the recursive call |sumList t|) is to blame.

>>>>

\mysection{Overview} \label{sec:overview}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{figure}[t!]
\begin{minipage}{0.45\linewidth}
\begin{ecode}
  let rec sumList xs =
    match xs with
    | []   -> (*@\hlTree{\hlSherrloc{[]}}@*)
    | h::t -> h (*@\hlTree{+}@*) (*@\hlFix{sumList t}@*)
\end{ecode}
\end{minipage}
\begin{minipage}{0.49\linewidth}
\begin{verbatim}
File "sumList.ml", line 4, characters 16-25:
  This expression has type 'a list
  but an expression was expected of type int
\end{verbatim}
\end{minipage}
\caption{(left) An ill-typed \ocaml program that should sum the elements of a
  list, with highlights indicating three possible blame assignments based on:
  %
  (1) the \hlFix{\ocaml} compiler;
  %
  (2) the \hlSherrloc{fix} made by the programmer; and
  %
  (3) \hlTree{minimizing} the number of edits required.
  % The \underline{underlined} expressions are equally valid
  % locations to blame. The expression blamed by the \ocaml compiler
  % is in \textbf{bold}.
  %
  % FIXME: This bolding is ambiguous, because ``let rec'', ``match'' and
  % ``with'' are also bolded (by \\ecode)! You need to find another way to
  % highlight what ocaml is yelling about.
  %
  (right) The error reported by \ocaml.}
\label{fig:sumList}
\end{figure}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

Lets start with an overview of \toolname's
approach to localizing type errors by
collectively learning from the mistakes
programmers actually make.

\mypara{The Problem}
%
Consider the |sumList| program in
\autoref{fig:sumList}, written by
a student in an undergraduate
Programming Languages course.
%
The program is meant to add up the
integers in a list, but the student
has accidentally given the empty
list as the base case, rather than |0|.
%
The \ocaml compiler collects typing
constraints as it traverses the program,
and reports an error the moment it finds
an inconsistent constraint.
%
In this case it blames the recursive call
to |sumList|, complaining that |sumList|
returns a |list| where an |int| was
expected by the |+| operator.
%
This \emph{blame} assignment is inconsistent
with the programmer's intention and may
not be helpful debugging information to
a novice.

It may appear obvious to the reader that
|[]| is the correct expression to blame,
but how is a type checker to know that?
%
Indeed, both the venerable
\ocaml compiler as well as
recent techniques like
\sherrloc and \mycroft~\citep{Zhang2014-lv,Loncaric2016-uk,Pavlinovic2014-mr}.
fail to distinguish between
the two underlined expressions
in \autoref{fig:sumList};
it would be equally valid
to blame \emph{either}
of them alone.
%
The |[]| on line 3 could be changed to |0|,
or the |+| on line 4 could be changed to
either |@| (list append) or |::|, all of
which would give type-correct programs.
%
Thus, these state-of-the-art techniques
are forced to either blame \emph{both}
locations, or choose one \emph{arbitrarily}.

\mypara{Error Localization via Supervised Classification}
%
Our approach is to view error localization as a
\emph{supervised classification}
problem~\citep{Kotsiantis2007-pj}.
%
A \emph{classification} problem entails learning
a function that maps \emph{inputs} to a discrete
set of output \emph{labels} (in contrast to, say,
\emph{regression}, where the output is typically
a real number.)
%
A \emph{supervised} learning problem is one where
we are given a \emph{training set} where the
inputs and labels are known, and the task is to
learn a function that accurately maps the inputs
to output labels and \emph{generalizes} to new,
yet-unseen inputs.
%
To realize the above approach for error localization
as a practical tool, we have to solve four sub-problems.
%
\begin{enumerate}
  \item How can we acquire a \emph{training set} of
        blame-labeled ill-typed programs?

  \item How can we \emph{represent} blame-labeled programs
        as numeric vectors amenable to machine learning?

  \item How can we find \emph{features} that yield predictive
        models?

  \item How can we use the models to give localized
        \emph{feedback} to the programmer?
\end{enumerate}

\mysubsection{Step 1: Acquiring a Blame-Labeled Training Set}

The first step is to create a training
set of ill-typed programs, where each
erroneous sub-term is explicitly labeled.
%
Prior work has often enlisted
expert users to curate a set of
ill-typed programs and then
\emph{manually} determine the
correct fix~\citep[\eg][]{Lerner2007-dt,Loncaric2016-uk}.
%
This method is suitable for evaluating
the quality of a localization (or repair)
algorithm on a small number (\eg, 10-100s)
of programs.
%
However, in general it requires a great
deal of effort for the expert to divine
the original programmers' intentions.
%
Consequently, is difficult to scale the
expert-labeling to yield a dataset large
enough (\eg, 1000s of programs) needed to
facilitate machine learning.
%
More importantly, this approach fails to
capture the \emph{frequency} with which
errors occur in practice.

We solve both the scale and frequency problems
by instead extracting blame-labeled data sets
from \emph{interaction traces}.
%
Software development is an iterative process.
Programmers, perhaps after a lengthy (and
sometimes frustrating) back-and-forth with
the type checker, eventually end up fixing
their own programs.
%
Thus, we implemented an instrumented
version of the \ocaml compiler that records
this conversation, \ie records the sequence
of programs submitted by each programmer and
whether or not it was deemed type-correct.
%
For each ill-typed program in
a particular programmer's trace,
we find the \emph{first subsequent}
program in the trace that type checks
and declare it to be the fixed version.
%
From this pair of an ill-typed program
and its fix, we can extract a \emph{diff}
of the abstract syntax trees, and then assign
the blame labels to the \emph{smallest}
sub-tree in the diff.

For example, suppose our student
fixed the |sumList| program in
\autoref{fig:sumList} by replacing
|[]| with |0|, the diff would
include only the |[]| expression.
%
Thus we would determine that the
|[]| expression (and \emph{not} the
|+| or the recursive call |sumList t|)
is to blame.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\mysubsection{Step 2: Representing Programs as Vectors}

\mysubsection{Step 3: Feature Discovery}

\mysubsection{Step 4: Generating Feedback}

% Evaluation

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\paragraph{\textbf{Challenge (1): How to represent programs?}}

The first and prime challenge we address is how to translate programs
into a format favorable to learning a model of type errors.
%
Programs can be represented in various ways, from the raw text to
richly-structured abstract syntax trees and control-flow graphs, but
many representations are not directly amenable to machine learning.
%
Furthermore, program representations that are amenable to one learning
task, \eg code completion, may not be favorable to our problem of
assigning blame for type errors.

@@

\paragraph{\textbf{Challenge (2): What is the ``correct'' expression to blame?}}
%
%% As we saw in \autoref{fig:sumList},
%% type errors admit many different
%% fixes to different expressions,
%% each resulting in a different program.
%% %
%% How is the type checker to judge
%% which expressions are more likely
%% to be incorrect than others?

\paragraph{\textbf{Solution: Use the students' subsequent fixes}}
%
Rather than relying on expert users, we follow
\citet{Zhang2014-lv} \RJ{CHECK} and allow our students to
do the work of assigning blame themselves.
%
Software development is an iterative process and our students
eventually fix their own programs, perhaps after multiple ill-fated
attempts.
